Last glacial cycle glacier erosion potential in the Alps \large \newline Supplementary figures

### 2021-06-11 articles/erosion/alps-erosion-supplement.tex
Add Rhine transect plots in supplement.

>>>>

    \begin{figure*}
      \centerline{\includegraphics{alpero_transects}}
      \caption[%
        Rhine Glacier potential erosion rate over time after
        \citet{Koppes.etal.2015}, same as main text Fig. 3.
      ]{%
        \textbf{(a--d)} Modelled instantaneous potential erosion rate of the
          Rhine Glacier for selected glacier advance and retreat ages, and the
          final model state for topographic reference.
        \textbf{(e)} Interpolated instantaneous potential erosion rate along a
          Rhine Glacier transect (upper panels dashed line) for the entire last
          glacial cycle.
        After \citet{Koppes.etal.2015}, same as main text Fig. 3.}
    \end{figure*}

    \begin{figure*}
      \includegraphics{alpero_transects_her2015}
      \caption{%
        Rhine Glacier potential erosion rate over time after
        \citet{Herman.etal.2015}.}
    \end{figure*}

    \begin{figure*}
      \includegraphics{alpero_transects_hum1994}
      \caption{%
        Rhine Glacier potential erosion rate over time after
        \citet{Humphrey.Raymond.1994}.}
    \end{figure*}

    \begin{figure*}
      \includegraphics{alpero_transects_coo2020}
      \caption{%
        Rhine Glacier potential erosion rate over time after
        \citet{Cook.etal.2020}.}
    \end{figure*}
